Thesis

### 2018-10-05 thesis/thesis.tex
draft1.1

\chapter{Introduction}
\section{First section}

Your text goes here.

@@

Pairing correlation plays important role near the Fermi energy. To examine the pairing dynamics influencing the structure of nuclei, we can only concentrate the nucleons near the Fermi energy. The Hamiltonian of pairing model is
\begin{align}
	H &= \sum_l \epsilon_l n_l - g \sum_{l,l'} S_l^+ S_{l'}^- ,
\end{align}
where
\begin{align}
	n_l &= \sum_m a^{\dag}_{lm}a_{lm} \\
        S_l^{+} &= \sum_{m>0}a_{lm}^{\dag}a_{l\overline{m}}^{\dag} ,
\quad   S_l^{-} = S_l^{+\dag} 
\end{align}

>>>>

\chapter{Introduction}

\section{Pairing interaction in nuclei}

Pairing correlation plays an important role near the Fermi energy. Pairing correlation is the two-body interaction which couples two identical nucleons into $J^{\pi}=0^+$ state. There are many evidences of pairing correlation detected from experiment. The most clear evidence is shown in Fig. \ref{Sn_isotope}. All of the ground states of even-even Sn isotopes are $J^{\pi}=0^+$ states  It indicates that the ground states consist of the $J^{\pi}=0^+$ pairs is more stable than other configurations. In addition, the ground states between even-even nuclei and neighborhood odd nuclei has large gaps of binding energy. In odd nuclei, the unpaired last neutron is the last single-particle level. The odd-even mass difference  To break the $J^{\pi}=0^+$ pair, we need large energy which is about $2\Delta \approx 24A^{-1/2}$ MeV.
\begin{figure}[htbp]
 \begin{center}
    \includegraphics[width=100mm, bb=0 0 400 300]{images/Sn_isotope.png}
 \end{center}
  \caption{Low-lying excited states in Sn isotopes \cite{}. The absolute values of binding energy are adjusted at 0 MeV in the ground state of ${}^{116}$Sn.}
  \label{Sn_isotope}
\end{figure}

@@

To examine the pairing dynamics influencing the structure of nuclei, we can only concentrate the nucleons near the Fermi energy. The Hamiltonian of pairing model is
\begin{align}
	H &= \sum_l \epsilon_l n_l - g \sum_{l,l'} S_l^+ S_{l'}^- ,
\end{align}
where
\begin{align}
	n_l &= \sum_m a^{\dag}_{lm}a_{lm} \\
        S_l^{+} &= \sum_{m>0}a_{lm}^{\dag}a_{l\overline{m}}^{\dag} ,
\quad   S_l^{-} = S_l^{+\dag} 
\end{align}
